\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-17 main.tex
Updates from Overleaf

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}. The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:device} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:ring-with-slit}(a) to view the resulting mesh. After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\mu\mathrm{m}$, outer diameter $3\,\mu\mathrm{m}$, and effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, interrupted by a slit of width $0.5\,\mu\mathrm{m}$. a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated by \inline{Device.plot()}. b) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated by \inline{Solution.plot_fields()}. c) Current density $\vec{J}$ in the ring, generated by \inline{Solution.plot_currents()}.}
    \label{fig:ring-with-slit}
\end{figure}

@@

A \SuperScreen model consists of 1) a \inline{Device} with a mesh, 2) a function or \inline{Parameter} that defines the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, 3) a value for the current circulating around each hole in the device due to trapped flux, and 4) a collection of vortices $v$ located at positions $\vec{r}_v$ and carrying flux $\Phi_v$. These items serve as the inputs to \SuperScreen's main solver function, \inline{superscreen.solve()}, which implements the calculation outlined in Section~\ref{section:implementation}. When simulating a device with more than one layer, one can specify the number of times to implement the iterative calculation described in Section~\ref{section:model:multilayer} in order to solve for the response of all layers self-consistently. One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming no interaction between layers. The \inline{Device.solve_dtype} attribute determines the \inline{numpy} floating point data type used by \inline{solve()}. The default data type is \inline{float64} (64-bit double-precision float, equivalent to Python's \inline{float} type), but one can, for instance, set \inline{device.solve_dtype = "float32"} to use 32-bit single-precision floats in order to save memory.

@@

The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, vortices, and calculated stream functions and magnetic fields for all layers in the device. A \inline{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \inline{Solution.grid_data()}: Interpolates the calculated stream functions $g(x, y)$, magnetic fields $\mu_0H_z(x, y)$, or current densities $\vec{J}(x, y)$, for each layer from the triangular mesh to a rectangular grid.
    }
    % \item{
    % \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    % }
    \item{
    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
    \item{
    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
    }
    \item{
    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See Section~\ref{section:examples:fluxoid} for more details.
    }
\end{itemize}
\inline{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).

One may wish to solve many models involving the same device while varying other aspects of the model, for example sweeping the applied field, circulating currents, vortex properties, or some parameter of one or more layers in the device. Fortunately, the mesh and large matrices described in Section~\ref{section:implementation} depend only on the geometry of the device parallel to the $x-y$ plane. This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, vortex properties, layer heights (vertical positions), and penetration depths.

@@

% See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:square-ring-results} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.

@@

Instances of \inline{superscreen.Device} and \inline{superscreen.Solution} can be saved to and loaded from disk using their respective \inline{to_file()} and \inline{from_file()} methods, making it straightforward to share models and simulation results. \inline{Layers}, \inline{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format. Functions and \inline{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using \inline{dill}~\cite{McKerns}. \inline{Numpy} arrays, such as the mesh itself and the computed stream functions and fields, are saved in the \inline{numpy} \inline{npz} file format. A \inline{list} of \inline{Solutions}, such as that returned by \inline{superscreen.solve()} can be saved/loaded all at once using \inline{save_solutions()} and \inline{load_solutions()}.

>>>>

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}. The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh. After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\mu\mathrm{m}$, outer diameter $3\,\mu\mathrm{m}$, and effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, interrupted by a slit of width $0.5\,\mu\mathrm{m}$. a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. b) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. c) Current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.}
    \label{fig:ring-with-slit}
\end{figure}

@@

A \SuperScreen model consists of 1) a \inline{Device} with a mesh, 2) a function or \inline{Parameter} that defines the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, 3) a value for the current circulating around each hole in the device due to trapped flux, and 4) a collection of vortices $v$ located at positions $\vec{r}_v$ and carrying flux $\Phi_v$. These items serve as the inputs to \SuperScreen's main solver function, \inline{superscreen.solve()}, which implements the calculation outlined in Section~\ref{section:implementation}. When simulating a device with more than one layer, one can specify the number of times to implement the iterative calculation described in Section~\ref{section:model:multilayer} in order to solve for the response of all layers self-consistently. One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming no interaction between layers. The \inline{device.solve_dtype} attribute determines the \inline{numpy} floating point data type used by \inline{solve()}. The default data type is \inline{float64} (64-bit double-precision float, equivalent to Python's \inline{float} type), but one can, for instance, set \inline{device.solve_dtype = "float32"} to use 32-bit single-precision floats in order to save memory.

@@

The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, vortices, and calculated stream functions and magnetic fields for all layers in the device. A \inline{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \inline{Solution.grid_data()}: Interpolates the calculated stream functions $g(x, y)$, magnetic fields $\mu_0H_z(x, y)$, or current densities $\vec{J}(x, y)$, for each layer from the triangular mesh to a rectangular grid.
    }
    % \item{
    % \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    % }
    \item{
    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
    \item{
    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
    }
    \item{
    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See Section~\ref{section:examples:fluxoid} for more details.
    }
\end{itemize}
\inline{Solutions} also have several visualization methods built in (see Code Block~\ref{code:device}, Figure~\ref{fig:ring-with-slit}, and Section~\ref{section:overview:visualization}).

One may wish to solve many models involving the same device while varying other aspects of the model, for example sweeping the applied field, circulating currents, vortex properties, or some parameter of one or more layers in the device. Fortunately, the mesh, Laplace operator, kernel matrix, etc. (described in Section~\ref{section:implementation}) depend only on the geometry of the device parallel to the $x-y$ plane. This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, vortex properties, layer $z$-positions, and penetration depths.

@@

See Code Block~\ref{code:device} and  Figure~\ref{fig:ring-with-slit} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.

@@

Instances of \inline{superscreen.Device} and \inline{superscreen.Solution} can be saved to and loaded from disk using their respective \inline{to_file()} and \inline{from_file()} methods, making it straightforward to store and share models and simulation results. \inline{Layers}, \inline{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format. Functions and \inline{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using the \inline{dill} package~\cite{McKerns}. \inline{Numpy} arrays, such as the mesh itself and the computed stream functions and fields, are saved in the \inline{numpy} \inline{npz} file format. A \inline{list} of \inline{Solutions}, such as that returned by \inline{superscreen.solve()} can be saved/loaded all at once using \inline{save_solutions()} and \inline{load_solutions()}.
